Statistical methods for relative quantification of post-translational modifications in global proteomics experiments

### 2021-09-23 main/MSstatsPTM_Main.tex
fixed typo in shigella results section

Two specific modified peptides, $TTP\_MOUSE|P22893_S178$ and $KI67\_MOUSE|E9PVX6_T215$, show the power of the proposed method.  The profile plot of modified peptide $TTP\_MOUSE|P22893_S178$ shows a large positive log fold change of $2.9$ between the WT\_Late and WT\_Uninfected conditions. However, the global profiling run shows a similar log fold change of $2.015$ between  the same conditions. This indicates that the abundance change in the modified peptide is nearly entirely due to changes in the global protein. When adjusting for the global protein the modified peptide's adjusted pvalue becomes insignificant, going from $.0009$ to $.275$. In contrast $KI67\_MOUSE|E9PVX6_T215$ originally shows a small positive log fold change of $.212$ between conditions WT\_Early and WT\_Uninfected. This is contrast with a negative fold change in the global profiling run of $-.616$. In adjusting the modified peptide for changes in the global protein, the log fold change becomes .828 and the adjusted pvalue goes from $.452$ to $.037$.

>>>>

Two specific modified peptides, $TTP\_MOUSE|P22893\_S178$ and $KI67\_MOUSE|E9PVX6\_T215$, show the power of the proposed method.  The profile plot of modified peptide $TTP\_MOUSE|P22893\_S178$ shows a large positive log fold change of $2.9$ between the WT\_Late and WT\_Uninfected conditions. However, the global profiling run shows a similar log fold change of $2.015$ between  the same conditions. This indicates that the abundance change in the modified peptide is nearly entirely due to changes in the global protein. When adjusting for the global protein the modified peptide's adjusted pvalue becomes insignificant, going from $.0009$ to $.275$. In contrast $KI67\_MOUSE|E9PVX6\_T215$ originally shows a small positive log fold change of $.212$ between conditions WT\_Early and WT\_Uninfected. This is contrast with a negative fold change in the global profiling run of $-.616$. In adjusting the modified peptide for changes in the global protein, the log fold change becomes .828 and the adjusted pvalue goes from $.452$ to $.037$.
